The Power of Two Random Choices

### 2013-11-07 article/article.tex
use acm template for article; fix footnote issue with acm template and missing bracket

\documentclass[a4paper,10pt, twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[usenames,dvipsnames]{color}
\usepackage{comment}
\usepackage{tikz}
\usepackage{verbatim}
\usetikzlibrary{arrows,shapes}
\usepackage{listings}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{tabularx}
\usepackage{enumitem}
\setlist{nolistsep}
\setlength{\parindent}{0cm}

%page boarders
\usepackage[top=3cm, bottom=3cm, left=2cm, right=2cm]{geometry}
\usepackage[style=numeric,backend=bibtex]{biblatex}
\addbibresource{../sources}

\newtheorem{lemma}{Lemma}
\newtheorem{corollary}[lemma]{Corollary}
\newtheorem{theorem}[lemma]{Theorem}

\title{The Power of Two Random Choices \\ 
\large A follow up seminar to the Parallel Algorithms lecture\footnote{Jesper Larsson Träff and Francesco Versaci, lecture "Parallel Algorithms", 2012 winter term at TU Wien.}}
\author{Martin Kalany, 0825673}

\begin{document}
\maketitle

\section{Abstract}
\label{sec:abstract}
\cite{mitzen01}

\section{Introduction}
\label{sec:intro}

%\pagebreak
\printbibliography
\end{document}

>>>>

\documentclass{acm_proc_article-sp}

%\newtheorem{lemma}{Lemma}
%\newtheorem{corollary}[lemma]{Corollary}
%\newtheorem{theorem}[lemma]{Theorem}

\begin{document}

\title{The Power of Two Random Choices}
\subtitle{\large A follow up seminar to the lecture "Parallel Algorithms"\\ by Jesper Larsson Tr\"aff and Francesco Versaci, 2012 winter term at TU Wien.}

\numberofauthors{1}
\author{
\alignauthor
Martin Kalany\\
       0825673
}    
\date{\today}

\maketitle
\begin{abstract}

\end{abstract}

\section{Introduction}
\cite{mitzen01}
\label{sec:intro}

%bibliography
\bibliographystyle{abbrv}
\bibliography{../sources} 
\end{document}
